Tutorial 2a

### 2025-07-06 Tutorial_2a.Rmd
update Tutorial 2a

Following Heiss (2021), we can plot the expected value of the posterior predictive distribution -- the predicted hazard values -- for the "average" participant at the population level, and for each participant in the data set.

@@

Following Heiss (2021), we are actually interested in the difference in predicted hazard between congruent and blank primes on the one hand, and between incongruent and blank primes on the other hand, for each time bin. When based on the grand mean, this is known as the grand average marginal effect (AME).

>>>>

Following Heiss (2021) -https://www.andrewheiss.com/blog/2021/11/10/ame-bayes-re-guide/#average-marginal-effects-, we can plot the expected value of the posterior predictive distribution -- the predicted hazard values -- for the "average" participant at the population level, and for each participant in the data set.

@@

Following Heiss (2021) - https://www.andrewheiss.com/blog/2021/11/10/ame-bayes-re-guide/#average-marginal-effects -, we are actually interested in the difference in predicted hazard between congruent and blank primes on the one hand, and between incongruent and blank primes on the other hand, for each time bin. When based on the grand mean, this is known as the grand average marginal effect (AME).
